Attachment Analysis: Report Project

### 2021-06-29 Documents/Report-Project/Attachment_Analysis_Report.Rmd
revision analysis cluster

# Cluster
drake::loadd(cluster_mother_tat)
drake::loadd(cluster_father_tat)
drake::loadd(data_cluster_tat)
drake::loadd(mclust_mother)
drake::loadd(mclust_father)

@@

### Externalizing
```{r}
ggplot(data_munged) +
  geom_bar(aes(x = externalizing_sum, fill = genere), alpha = 0.7) +
  facet_grid(genere ~ .)
```

### Internalizing
```{r}
ggplot(data_munged) +
  geom_bar(aes(x = internalizing_sum, fill = genere), alpha = 0.7) +
  facet_grid(genere ~ .)
```

@@

```{r}
plot(cluster_mother_tat, main = "Dendrogramma")
rect.hclust(cluster_mother_tat, k=4, border="red")
```

@@

```{r, echo = TRUE}
table(data_cluster_tat$cluster_mother_tat)

prop.table(table(data_cluster_tat$cluster_mother_tat))

prop.table(table(data_cluster_tat$cluster_mother_tat,
                 data_cluster_tat$genere),2)

summary(table(data_cluster_tat$cluster_mother_tat,
              data_cluster_tat$genere))
```

@@

```{r}
plot_scores_mother(data = data_cluster_tat)
```

@@

```{r}
plot(cluster_father_tat, main = "Dendrogramma")
rect.hclust(cluster_father_tat, k=4, border="red")
```

@@

```{r, echo = TRUE}
table(data_cluster_tat$cluster_father_tat)

prop.table(table(data_cluster_tat$cluster_father_tat))

prop.table(table(data_cluster_tat$cluster_father_tat,
                 data_cluster_tat$genere),2)

summary(table(data_cluster_tat$cluster_father_tat,
              data_cluster_tat$genere))
```

@@

```{r}
plot_scores_father(data = data_cluster_tat)
```

@@

```{r, echo = TRUE}
brms::get_prior(brms::bf(
      internalizing_sum ~ genere + cluster_mother_tat + cluster_father_tat,
      zi ~ genere + cluster_mother_tat + cluster_father_tat),
      data = data_cluster_tat,
      family = brms::zero_inflated_poisson())
```

>>>>

# Cluster
drake::loadd(cluster_mother_fit)
drake::loadd(cluster_father_fit)
drake::loadd(data_cluster)
drake::loadd(mclust_mother)
drake::loadd(mclust_father)

@@

### Externalizing
```{r}
ggplot(data_munged) +
  geom_bar(aes(x = externalizing_sum, fill = gender), alpha = 0.7) +
  facet_grid(gender ~ .)
```

### Internalizing
```{r}
ggplot(data_munged) +
  geom_bar(aes(x = internalizing_sum, fill = gender), alpha = 0.7) +
  facet_grid(gender ~ .)
```

@@

```{r}
plot(cluster_mother_fit, main = "Dendrogramma")
rect.hclust(cluster_mother_fit, k=4, border="red")
```

@@

```{r, echo = TRUE}
table(data_cluster$cluster_mother)

prop.table(table(data_cluster$cluster_mother))

prop.table(table(data_cluster$cluster_mother,
                 data_cluster$gender),2)

summary(table(data_cluster$cluster_mother,
              data_cluster$gender))
```

@@

```{r}
plot_scores_mother(data = data_cluster)
```

@@

```{r}
plot(cluster_father_fit, main = "Dendrogramma")
rect.hclust(cluster_father_fit, k=4, border="red")
```

@@

```{r, echo = TRUE}
table(data_cluster$cluster_father)

prop.table(table(data_cluster$cluster_father))

prop.table(table(data_cluster$cluster_father,
                 data_cluster$gender),2)

summary(table(data_cluster$cluster_father,
              data_cluster$gender))
```

@@

```{r}
plot_scores_father(data = data_cluster)
```

@@

```{r, echo = TRUE}
brms::get_prior(brms::bf(
      internalizing_sum ~ gender + cluster_mother + cluster_father,
      zi ~ gender + cluster_mother + cluster_father),
      data = data_cluster,
      family = brms::zero_inflated_poisson())
```
